### 2023-07-12 calculus.tex
Fix some typos

Then, \cref{thm:calculus-marking-well-formedness} provides the necessary
\emph{well-formedness} criterion for marking.
%
\begin{theorem}[name=Marking Well-Formedness] \
  \label{thm:calculus-marking-well-formedness}
  \begin{enumerate}
    \item If $\ctxSynFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}$, then 
      $\erasesTo{\ECMV}{\EMV}$.
    \item If $\ctxAnaFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}$, then  and
      $\erasesTo{\ECMV}{\EMV}$.
  \end{enumerate}
\end{theorem}
%

@@

Now, to define analytic marking on forms without explicit analytic typing rules, we also need
subsumption rules for marking and marked expression typing. Note that we define a analogous notion
of ``subsumability'' for marked expressions, written $\subsumable{\ECMV}$.
%
\begin{mathpar}
  \judgment{
    \ctxSynFixedInto{\ctx}{\EMV}{\ECMV}{\TMV'} \\
    \consistent{\TMV}{\TMV'} \\
    \subsumable{\EMV}
  }{
    \ctxAnaFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}
  }{MKASubsume}

@@

Note that in this example language, the distinction from the inconsistent type mark is of reduced
significance---all expressions synthesize a type. However, the addition of unannotated lambda
abstractions, for example, would necessitate such a disctinction.

>>>>

Then, \cref{thm:calculus-marking-well-formedness} provides the necessary
\emph{well-formedness} criterion for marking.
%
\begin{theorem}[name=Marking Well-Formedness] \
  \label{thm:calculus-marking-well-formedness}
  \begin{enumerate}
    \item If $\ctxSynFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}$, then 
      $\erasesTo{\ECMV}{\EMV}$.
    \item If $\ctxAnaFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}$, then
      $\erasesTo{\ECMV}{\EMV}$.
  \end{enumerate}
\end{theorem}
%

@@

Now, to define analytic marking on forms without explicit analytic typing rules, we also need
subsumption rules for marking and marked expression typing. Note that we define an analogous notion
of ``subsumability'' for marked expressions, written $\subsumable{\ECMV}$.
%
\begin{mathpar}
  \judgment{
    \ctxSynFixedInto{\ctx}{\EMV}{\ECMV}{\TMV'} \\
    \consistent{\TMV}{\TMV'} \\
    \subsumable{\EMV}
  }{
    \ctxAnaFixedInto{\ctx}{\EMV}{\ECMV}{\TMV}
  }{MKASubsume}

@@

Note that in this example language, the distinction from the inconsistent type mark is of reduced
significance---all expressions synthesize a type. However, the addition of unannotated lambda
abstractions, for example, would necessitate such a distinction.
